Computing in the Field of Rationals

### 2012-06-23 rational_ext.tex
_

@@

>>>>

\paragraph*{Annihilation.} 
A consequence of the semantics is that they admit computations that
are undefined. For instance consider, where {{not : bool <-> bool}}.

{{eta* (;) (id (*) not) (;) eps* : 1 <-> 1}}

Tracing this circuit gives us:

%subcode{opsem} include main
%! columnStyle = rllr
% & & <eta* (;) (id (*) not) (;) eps*, (), []>
% & |-->* & <eta*, (), Fst [] (id (*) not) (;) eps*>
% (1) & |--> & [eta*, (1/true, true), Fst [] (id (*) not) (;) eps*] 
% & |-->* & <not, true, RightT id 1/true (Fst (Snd~eta* []) ~eps*)> 
% & |-->* & [not, false, RightT id 1/true (Fst (Snd~eta* []) ~eps*)] 
% & |-->* & [eps*, (1/true, false), Snd (id (*) not) (Snd~eta* [])]
% & |--> & undefined
% (2) & |--> & [eta*, (1/false, false), Fst [] (id (*) not) (;) eps*] 
% & |-->* & <not, false, RightT id 1/false (Fst (Snd~eta* []) ~eps*)> 
% & |-->* & [not, true, RightT id 1/false (Fst (Snd~eta* []) ~eps*)] 
% & |-->* & [eps*, (1/false, true), Snd (id (*) not) (Snd~eta* [])]
% & |--> & undefined

@@

\begin{proof}
  We briefly summarize the execution of the first combinator (let us
  call it {{c}}) combinator to show that the coherence conditions
  hold.
\item

%subcode{opsem} include main
%! columnStyle = rllr
% & & <c, v:b, []>
% & |-->* & <eta*, (), C1>
% & |-->  & <eta*, (1/v',v'), C2> & some v':b
% & |-->* & <eps*, (1/v', v), C3> & when v' = v
% (1) & |-->~ & [eps*, (), C3]
% & |-->* & [c', v, [] ]
% (2) & |-->* & <eps*, (1/v', v), C3> & when v' /= v
% & |-->~ & undefined

Thus for {{v:b}}, the evaluation of {{<c, v, []>}} always produces {{v:b}} as
output, i.e. {{c = id}}.
